Kamala Harris Rises as the 2024 Election Front Runner: A Poll-of-Polls Forecast

### 2024-10-24 paper/paper.qmd
recent polling data update

(Data last updated on 22 Oct 2024.) - [!!! MODIFY AT FINAL !!!]

@@

The original dataset sourced from FiveThirtyEight [@fivethirtyeight2024] aggregates a wide range of poll results (16012 observations, based on dataset available at Oct 22, 13:00). The polls conducted by various polling organizations capture voter preferences by taking a representative sample of the electorate and asking for the voters' candidate of choice. Surveys were conducted at the state and national levels, providing the wide perspective on public feelings across the country.

>>>>

(Data last updated on 24 Oct 2024.) - [!!! MODIFY AT FINAL !!!]

@@

The original dataset sourced from FiveThirtyEight [@fivethirtyeight2024] aggregates a wide range of poll results (16264 observations, based on dataset available at Oct 24, 13:00). The polls conducted by various polling organizations capture voter preferences by taking a representative sample of the electorate and asking for the voters' candidate of choice. Surveys were conducted at the state and national levels, providing the wide perspective on public feelings across the country.
